---
title: "Access to Care by State"
output: blastula::blastula_email
---

#  Access to Care 
## `r params$state`

### County Map - Hospital Coverage

Breakdown of counties and their status based on county population compared to 
the number of hospitals

```{r}
atc_plot_state_map(state = params$state)
```

### Counties Under or Over the exepected number of hospitals

```{r}
us_counties |> 
  filter(state_name == params$state, pred_status == "below") |> 
  select(county_name, hospitals, population, pred_lwr, pred_fit) |> 
  gt() |> 
  fmt_number(
    columns = population,
    suffixing = TRUE
  ) |> 
  cols_label(
    "county_name" = "County", 
    "hospitals" = "Hospitals", 
    "population" = "Population",
    "pred_lwr" = "Least Expected",
    "pred_fit" = "Ideally Expected"
    )
```

### Background

We are trying to determine which counties in **`r params$state`** have 
comparatively more access or less access to hospital care. A **statistical
model using data from across the country** is used to identify those counties 
that have more or less than the model expects the specific county to have.

