---
title: "Access to Care by State"
output:
  pdf_document:
    df_print: kable
params:
  state:
    label: "State:"
    value: California
    input: select
    choices: [Alabama, Arizona, Arkansas, California, Colorado, Connecticut, Delaware, District of Columbia, Florida, Georgia, Hawaii, Idaho, Illinois, Indiana, Iowa, Kansas, Kentucky, Louisiana, Maine, Maryland, Massachusetts, Michigan, Minnesota, Mississippi, Missouri, Montana, Nebraska, Nevada, New Hampshire, New Jersey, New Mexico, New York, North Carolina, North Dakota, Ohio, Oklahoma, Oregon, Pennsylvania, Rhode Island, South Carolina, South Dakota, Tennessee, Texas, Utah, Vermont, Virginia, Washington, West Virginia, Wisconsin, Wyoming]
  printcode:
    label: "Display Code:"
    value: FALSE
always_allow_html: yes    
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = params$printcode)

library(accesstocare)
library(dplyr)
library(gt)
```

## `r params$state`

### Background

We are trying to determine which counties in **`r params$state`** have comparatively more access or less access to hospital care.

A **statistical model using data from across the country** is used to identify those counties that have more or less than the model expects the specific county to have.

### County Map

Breakdown of counties and their status based on county population compared to the number of hospitals

```{r, fig.height = 7, fig.width = 9}
atc_plot_state_map(state = params$state)
```

### County Data

Here is the county level data used in this report

```{r}
us_counties %>% 
  filter(state_name == params$state) %>% 
  select(county_name, hospitals, population) %>% 
  gt() %>% 
  fmt_number(
    columns = population,
    suffixing = TRUE
  ) %>% 
  cols_label("county_name" = "County", "hospitals" = "Hospitals", "population" = "Population")
```
