---
title: "Access to Care by State"
params:
  state: California
output: email
---

```{r}
#| include: false

library(accesstocare)
library(dplyr)
library(DT)
library(gt)
```

## `r params$state`

### Background

We are trying to determine which counties in **`r params$state`** have comparatively more access or less access to hospital care.

A **statistical model using data from across the country** is used to identify those counties that have more or less than the model expects the specific county to have.

### County Map

Breakdown of counties and their status based on county population compared to the number of hospitals

```{r}
#| fig-height: 7
#| fig-width: 9
atc_plot_state_map(state = params$state)
```

### County Data

Here is the county level data used in this report

```{r}
us_counties %>% 
  filter(state_name == params$state) %>% 
  select(county_name, hospitals, population) %>% 
  datatable(colnames = c("County" = "county_name", "Hospitals" = "hospitals", "Population" = "population"))
```

::: {.email}

::: {.subject}
Access to Care - `r params$state`
:::

#  Access to Care 
## `r params$state`

### County Map - Hospital Coverage

Breakdown of counties and their status based on county population compared to the number of hospitals

```{r}
atc_plot_state_map(state = params$state)
```
:::